Validation of Visual Statistical Inference, Applied to Linear Models

### 2012-06-10 paper_jasa.tex
summary table for minimum p-value assumption

@@

>>>>

\begin{table}[hbtp]
\caption{Number of lineups for which most people pick the plot with minimum $p$-value. The data used is from screening criteria 1. \blue{Is this table useful? I can do the same for all the screening criteria.}} 
\begin{center}
\begin{tabular}{rrr}
  \hline
  Experiment & Total lineups & most  pick minimum $p$-value\\ 
  \hline
1 &   60 &  37 \\ 
  2 &   70 &  60 \\ 
   \hline
\end{tabular}
\end{center}
\end{table}

@@

\begin{figure*}[hbtp]
   \centering
       \scalebox{0.5}{\includegraphics{p_val_log_counts2.pdf}}
       \caption{Frequency of plot picks by log$_10$ $p$-value in all of the seventy (70) individual lineups for experiment 2. The colored lines indicate the $p$-value of observed data plot.}
       \label{fig:P-val_log2}
\end{figure*}
